---
title: "Eating Out"
author: "javalos16"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

I will be going over analytical data, showing the differences in white, black and other races eating out? 

## There were two years in which the General Social Survey asked about the frequency of eating out.
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```

```{r, eval=TRUE,include=FALSE}
GSS <-readstata13::read.dta13(file="GSS1996.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

# Method

The variable of the problem iscat within races and numerical is the data in eating out.

# Decriptive Results

The graph will show what race eats out more than the other between white, black and other.

## Graphical Results

```{r}
barchartGC(~race+eatout,data=mydata)
barchartGC(~race+eatout,data=mydata,type="percent")
```
This graph shows the differences in eating out between white, black and other races.


## Numerical description

```{r}
table1 <- xtabs(~race + eatout,data=mydata)
rowPerc(table1)
colPerc(table1)
```
The results in this numerical descriptions, shows the frequency of eating out in white ethnicity comparred to black and other ethnicity. Data is showing that white ethnicity frequency eat out more than black and other ethnicity.

```{r}
chisq.test(table1)

chisqtestGC(table1)

# Inferential results
fisherXY(mydata$race,mydata$eatout,printAll=T)
```


Chi square test shows the p value is so small that we reject the null hypothesis.
The fisherxy shows that the differences in white, black and other races in eating out. Data shows that there is a difference in eating in white, black and other races.

# Discussion and Conclusion

Based on the results,we reject the null hypothesis the p-value is so small that, the differences in frequency of eating out. I reject the null hypothesis based on the result.